<!--
================================================================================
behavioural_analysis.Rmd — Model-free behavioural analysis and figures
================================================================================
Aim:     Reproduces the model-free (non-DDM) behavioural results and figures:
         complex-choice proportions and response times in the CS condition,
         risky/EV-consistent choice and RT in the CCSS condition, paired
         t-tests, and mixed-effects (glmer) EV-sensitivity models. Produces the
         combined per-study behavioural figures (full_combined_*.pdf).

Inputs:  The three derived per-study data sets. In this package the equivalent
         data are in ../data/ :
             number_of_outcome  -> Study 1  (../data/final_df_study1.rds)
             outcome-as-term    -> Study 2  (../data/final_df_study2.rds)
             compound_prob      -> Study 3  (../data/final_df_study3.rds)
         Set `study_paths` (in the "Load data" chunk below) to these files.
         The RDS files are already pre-processed (skew recoding, response flip,
         RT in seconds, test-trial filter) — no further pre-processing is done here.

Outputs: full_combined_number_of_outcome.pdf / _outcome-as-term.pdf /
         _compound_prob.pdf (choice + RT panels per study), plus printed
         t-tests and model summaries.

Usage:   Open in RStudio and knit, or run chunk by chunk. Requires:
         dplyr, tidyr, ggplot2, purrr, cowplot, lme4, performance.

Part of the complexity-under-risk replication package (behavioural analysis).
Pipeline order and dependencies are documented in ../README.md.
================================================================================
-->
```{r}
# Load required libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(cowplot)

# Helper: mean and 95% CI via t.test (returns NA bounds if all values identical)
calculate_mean_ci <- function(data) {
  if (length(unique(data)) == 1) {
    return(list(mean = mean(data), lower = NA, upper = NA))
  }
  t_result <- t.test(data)
  return(list(mean = mean(data), lower = t_result$conf.int[1], upper = t_result$conf.int[2]))
}

# Helper: paired t-test of (a - b) with effect size and a APA-style
# significance label. Returns a one-row data frame; replaces the three previous
# perform_t_test definitions.
paired_t_test_summary <- function(a, b, study_label) {
  t_test    <- t.test(a, b, paired = TRUE, alternative = "two.sided")
  diff      <- a - b
  mean_diff <- mean(diff, na.rm = TRUE)
  sd_diff   <- sd(diff, na.rm = TRUE)
  data.frame(
    study        = study_label,
    mean_diff    = mean_diff,
    t_statistic  = unname(t_test$statistic),
    df           = unname(t_test$parameter),
    p_value      = t_test$p.value,
    ci_lower     = t_test$conf.int[1],
    ci_upper     = t_test$conf.int[2],
    cohen_d      = mean_diff / sd_diff,
    significance = case_when(
      t_test$p.value < 0.001 ~ "***",
      t_test$p.value < 0.01  ~ "**",
      t_test$p.value < 0.05  ~ "*",
      TRUE                   ~ "ns"
    )
  )
}

# Output directory for all plots produced by this notebook
dir.create("behavioural_analysis", showWarnings = FALSE)

# --- Load data ---
# The RDS files use folder-based labels rather than the old "Study 1/2/3" naming.
# The pre-processing already applied in the RDS files (skew recoding, true_response
# flip via risk_index, /1000 RT conversion, test-trial filter) is not re-done here.
study_paths <- c(
  compound_prob     = "compound_prob/data/derived/final_df_study3.rds",
  `outcome-as-term` = "outcome-as-term/data/derived/final_df_study2.rds",
  number_of_outcome = "number_of_outcome/data/derived/final_df_study1.rds"
)
study_names <- names(study_paths)

data_compound_prob     <- readRDS(study_paths[["compound_prob"]])
data_outcome_as_term   <- readRDS(study_paths[["outcome-as-term"]])
data_number_of_outcome <- readRDS(study_paths[["number_of_outcome"]])

# Choice proportion processing
process_data_choice <- function(data, condition_label) {
  cleaned <- data %>%
    filter(skew_level %in% c('right_vs_left', 'left_vs_right', 'no_skew_vs_no_skew'),
           test_part %in% c('cs', 'sc')) %>%
    mutate(cho = ifelse(true_response == 'f', 1, -1),
           oa_complex = ifelse(test_part == 'cs', 1, -1),
           EV_diff = EV_diff * oa_complex,
           choosing_complex = ifelse((oa_complex == 1 & cho == 1) | (oa_complex == -1 & cho == -1), 1, 0)
    )

  individual <- cleaned %>%
    group_by(subject) %>%
    summarise(prop_complex = mean(choosing_complex, na.rm = TRUE)) %>%
    mutate(condition = condition_label)

  group <- individual %>%
    summarise(
      mean_prop_complex = mean(prop_complex),
      sd_prop_complex = sd(prop_complex),
      lower = mean(prop_complex) - 1.96 * sd_prop_complex / sqrt(n()),
      upper = mean(prop_complex) + 1.96 * sd_prop_complex / sqrt(n())
    ) %>%
    mutate(condition = condition_label)

  t_result <- t.test(individual$prop_complex, mu = 0.5)
  group <- group %>%
    mutate(
      t_value = t_result$statistic,
      df = t_result$parameter,
      p_value = t_result$p.value,
      ci_lower = t_result$conf.int[1],
      ci_upper = t_result$conf.int[2],
      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      )
    )

  list(individual = individual, group = group)
}

data_cp_summary  <- process_data_choice(data_compound_prob,     "compound_prob")
data_oat_summary <- process_data_choice(data_outcome_as_term,   "outcome-as-term")
data_no_summary  <- process_data_choice(data_number_of_outcome, "number_of_outcome")

individual_summary <- bind_rows(data_cp_summary$individual, data_oat_summary$individual, data_no_summary$individual)
group_summary      <- bind_rows(data_cp_summary$group,      data_oat_summary$group,      data_no_summary$group)

# RT processing
process_data_rt <- function(data, study_label) {
  cleaned <- data %>%
    filter(test_part %in% c('cs', 'sc') & skew_level != "catch") %>%
    mutate(cho = ifelse(true_response == 'f', 1, -1),
           choosing_complex = ifelse((cho == 1 & test_part == 'cs') | (cho == -1 & test_part == 'sc'), 1, 0)
    )

  filtered <- cleaned %>%
    group_by(subject) %>%
    filter(all(c(0, 1) %in% choosing_complex)) %>%
    ungroup()

  individual <- filtered %>%
    group_by(subject, choosing_complex) %>%
    summarise(median_rt = median(rt), .groups = "drop") %>%
    pivot_wider(names_from = choosing_complex, values_from = median_rt, names_prefix = "median_rt_") %>%
    mutate(median_rt_diff = median_rt_1 - median_rt_0,
           condition = 'Complex vs. Simple',
           study = study_label)

  summary <- individual %>%
    summarise(
      median_complex_rt_diff = calculate_mean_ci(median_rt_diff)$mean,
      lower = calculate_mean_ci(median_rt_diff)$lower,
      upper = calculate_mean_ci(median_rt_diff)$upper
    ) %>%
    mutate(condition = 'Complex vs. Simple', study = study_label)

  list(individual = individual, summary = summary)
}

results_cp  <- process_data_rt(data_compound_prob,     "compound_prob")
results_oat <- process_data_rt(data_outcome_as_term,   "outcome-as-term")
results_no  <- process_data_rt(data_number_of_outcome, "number_of_outcome")

combined_individual <- bind_rows(results_cp$individual, results_oat$individual, results_no$individual)
combined_summary    <- bind_rows(results_cp$summary,    results_oat$summary,    results_no$summary)

# Paired t-tests for the CS-condition RT (complex - simple)
t_test_results <- bind_rows(
  paired_t_test_summary(results_cp$individual$median_rt_1,  results_cp$individual$median_rt_0,  "compound_prob"),
  paired_t_test_summary(results_oat$individual$median_rt_1, results_oat$individual$median_rt_0, "outcome-as-term"),
  paired_t_test_summary(results_no$individual$median_rt_1,  results_no$individual$median_rt_0,  "number_of_outcome")
) %>%
  mutate(
    condition    = "Complex vs. Simple",
    Mean_Complex = c(mean(results_cp$individual$median_rt_1),
                     mean(results_oat$individual$median_rt_1),
                     mean(results_no$individual$median_rt_1)),
    Mean_Simple  = c(mean(results_cp$individual$median_rt_0),
                     mean(results_oat$individual$median_rt_0),
                     mean(results_no$individual$median_rt_0)),
    sd_Complex   = c(sd(results_cp$individual$median_rt_1),
                     sd(results_oat$individual$median_rt_1),
                     sd(results_no$individual$median_rt_1)),
    sd_Simple    = c(sd(results_cp$individual$median_rt_0),
                     sd(results_oat$individual$median_rt_0),
                     sd(results_no$individual$median_rt_0))
  )
t_test_results
```


```{r}
# theme: compact, thin axes, no grid, sans-serif body
theme_psyrev <- theme_classic(base_size = 10) +
  theme(
    text             = element_text(color = "black"),
    plot.title       = element_text(size = 10, face = "bold", hjust = 0,
                                    margin = margin(b = 4)),
    axis.title       = element_text(size = 9.5, color = "black"),
    axis.text        = element_text(size = 8.5, color = "black"),
    axis.line        = element_line(linewidth = 0.4, color = "black"),
    axis.ticks       = element_line(linewidth = 0.4, color = "black"),
    strip.background = element_rect(fill = "gray92", color = NA),
    strip.text       = element_text(size = 9.5, face = "bold"),
    legend.position  = "bottom",
    legend.title     = element_text(size = 9),
    legend.text      = element_text(size = 8.5),
    legend.key.size  = unit(0.35, "cm"),
    legend.margin    = margin(0, 0, 0, 0),
    plot.margin      = margin(4, 6, 4, 6)
  )

# Shared geom constants — keep all panels visually consistent
sig_text_size <- 2.5     # mm; in-panel asterisks
point_size    <- 0.7
point_alpha   <- 0.4     # individual jittered points
mean_size     <- 1.6     # filled black mean marker on top of the errorbar
err_w         <- 0.15    # error-bar cap width
err_lw        <- 0.7     # error-bar linewidth (thick enough to read over the cloud)
hline_lw      <- 0.3     # reference-line linewidth
bracket_lw    <- 0.3     # significance-bracket linewidth
trial_palette <- c(cc = "#298c8c", ss = "#f1a226")

combine_choice_rt_plot <- function(study_name) {
  group_choice <- group_summary       %>% filter(condition == study_name)
  ind_choice   <- individual_summary  %>% filter(condition == study_name)
  group_rt     <- combined_summary    %>% filter(study == study_name)
  ind_rt       <- combined_individual %>% filter(study == study_name)
  rt_sig       <- t_test_results      %>% filter(study == study_name)

  plot_choice <- ggplot() +
    geom_point(data = ind_choice,
               aes(x = "Complex vs. Simple", y = prop_complex),
               color = "black", position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha) +
    geom_errorbar(data = group_choice,
                  aes(x = "Complex vs. Simple", ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = group_choice,
               aes(x = "Complex vs. Simple", y = mean_prop_complex),
               size = mean_size, color = "black") +
    geom_text(data = group_choice,
              aes(x = "Complex vs. Simple", y = 0.92, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0.5, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = NULL, y = "Complex choice proportion") +
    ggtitle("(a) Complex choice proportion") +
    theme_psyrev + ylim(0, 1)

  plot_rt <- ggplot() +
    geom_point(data = ind_rt,
               aes(x = condition, y = median_rt_diff),
               color = "black", position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha) +
    geom_errorbar(data = group_rt,
                  aes(x = condition, ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = group_rt,
               aes(x = condition, y = median_complex_rt_diff),
               size = mean_size, color = "black") +
    geom_text(data = rt_sig,
              aes(x = condition, y = 4.5, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = NULL, y = "RT difference (complex − simple) [s]") +
    ggtitle("(b) RT difference") +
    theme_psyrev + ylim(-3, 6)

  list(cs_choice = plot_choice, cs_rt = plot_rt)
}
```

### ccss

Two-sided two-sample t test comparing the median participant response time in simple versus simple condition against complex versus complex condition.
We expect faster response times in simple versus simple condition than in complex versus complex condition.



```{r}
library(dplyr)
library(ggplot2)

# Function to process and summarize each dataset
process_response_times <- function(data, study_label) {
  cleaned_data <- data %>%
    filter(skew_level %in% c('right_vs_left', 'left_vs_right', 'no_skew_vs_no_skew')) %>%
    filter(test_part == 'cc' | test_part == 'ss')

  # Calculate median RT per participant for both cc and ss
  participant_median_rts <- cleaned_data %>%
    group_by(subject, test_part) %>%
    dplyr::summarize(median_rt = median(rt, na.rm = TRUE), .groups = "drop")

  # Spread the data to have cc and ss in separate columns for each participant
  participant_rts_wide <- participant_median_rts %>%
    pivot_wider(names_from = test_part, values_from = median_rt)

  # Calculate the difference between cc and ss for each participant
  participant_rts_wide <- participant_rts_wide %>%
    mutate(rt_difference = cc - ss)

  participant_means <- participant_rts_wide

  # Calculate group-level mean and confidence intervals for the difference
  mean_rt_group <- participant_means %>%
    dplyr::summarize(
      mean_rt_diff = calculate_mean_ci(rt_difference)$mean,
      lower = calculate_mean_ci(rt_difference)$lower,
      upper = calculate_mean_ci(rt_difference)$upper,
      .groups = "drop"
    ) %>%
    mutate(study = study_label)

  list(participant_means = participant_means, mean_rt_group = mean_rt_group)
}


```



```{r}
# Apply the function to each dataset
results_rt_cp  <- process_response_times(data_compound_prob,     "compound_prob")
results_rt_oat <- process_response_times(data_outcome_as_term,   "outcome-as-term")
results_rt_no  <- process_response_times(data_number_of_outcome, "number_of_outcome")

# Combine the results
combined_participant_means <- bind_rows(
  results_rt_cp$participant_means  %>% mutate(study = "compound_prob"),
  results_rt_oat$participant_means %>% mutate(study = "outcome-as-term"),
  results_rt_no$participant_means  %>% mutate(study = "number_of_outcome")
)

combined_mean_rt_group <- bind_rows(
  results_rt_cp$mean_rt_group,
  results_rt_oat$mean_rt_group,
  results_rt_no$mean_rt_group
)


```




```{r}
# CCSS RT: paired t-test cc vs ss for each study
t_test_results_rt <- bind_rows(
  paired_t_test_summary(results_rt_cp$participant_means$cc,  results_rt_cp$participant_means$ss,  "compound_prob"),
  paired_t_test_summary(results_rt_oat$participant_means$cc, results_rt_oat$participant_means$ss, "outcome-as-term"),
  paired_t_test_summary(results_rt_no$participant_means$cc,  results_rt_no$participant_means$ss,  "number_of_outcome")
)

t_test_results_rt
```





The interaction between EV_diff and condition in a generalized linear mixed model with EV_diff and condition as IV and choice as DV
We expect significant interaction between EV_diff and condition.



```{r}
library(lme4)
library(ggplot2)
library(dplyr)
library(performance)  # For R² calculations

# Function to fit the model, generate predictions, and extract important statistics
process_consistency <- function(data, study_label) {
  test_consistency <- data %>%
    filter(skew_level %in% c('right_vs_left', 'left_vs_right', 'no_skew_vs_no_skew')) %>%
    filter(test_part == 'ss' | test_part == 'cc') %>%
    mutate(risky = ifelse(true_response == 'f', 1, 0))

  # Fit the multilevel logistic regression model
  model <- glmer(
    risky ~ test_part + EV_diff  + test_part * EV_diff + (1 + EV_diff | subject),
    data = test_consistency,
    family = binomial(link = "logit"),
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
  )


  # Extract model statistics
  model_summary <- summary(model)
  coefficients <- as.data.frame(model_summary$coefficients)
  coefficients$predictor <- rownames(coefficients)



  # Store model statistics
  model_stats <- coefficients %>%
    rename(
      estimate = Estimate,
      std_error = `Std. Error`,
      z_value = `z value`,
      p_value = `Pr(>|z|)`
    ) %>%
    mutate(
      study = study_label,
      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      )
    ) %>%
    select(study, predictor, estimate, std_error, z_value, p_value, significance)


  # Predict probabilities and compute confidence intervals
  predictions <- predict(model, newdata = test_consistency, type = "link", se.fit = TRUE, re.form = NA)
  test_consistency <- test_consistency %>%
    mutate(
      predicted_risk = plogis(predictions$fit),
      lower_ci = plogis(predictions$fit - 1.96 * predictions$se.fit),
      upper_ci = plogis(predictions$fit + 1.96 * predictions$se.fit),
      study = study_label
    )

  list(data = test_consistency, coefficients = model_stats)
}

# Process all three datasets
results_cons_cp  <- process_consistency(data_compound_prob,     "compound_prob")
results_cons_oat <- process_consistency(data_outcome_as_term,   "outcome-as-term")
results_cons_no  <- process_consistency(data_number_of_outcome, "number_of_outcome")

# Combine all processed datasets
combined_consistency <- bind_rows(
  results_cons_cp$data,
  results_cons_oat$data,
  results_cons_no$data
)

# Combine model coefficients summary
interaction_summary <- bind_rows(
  results_cons_cp$coefficients,
  results_cons_oat$coefficients,
  results_cons_no$coefficients
)

# Filter interaction_summary to only keep the interaction effect
interaction_effect_summary <- interaction_summary %>%
  filter(predictor == "test_partss:EV_diff")

# Display only the interaction effect
interaction_effect_summary

```




Two-sided two-sample t test comparing participant-level frequency of dominant choices in catch trials in simple versus simple condition against complex versus complex condition.
We expect more dominant choices in simple versus simple condition than in complex versus complex condition.


```{r}
library(dplyr)

# Define a function to clean and process the data
process_study_data <- function(data) {
  cleaned_data <- data %>%
    select(subject, test_part, true_response, EV_diff, skew_level) %>%
    filter(skew_level == "catch") %>%
    mutate(accuracy = case_when(
      EV_diff > 0 & true_response == 'f' ~ 1,
      EV_diff < 0 & true_response == 'j' ~ 1,
      TRUE ~ 0
    )) %>%
    mutate(test_part = ifelse(test_part == "sc", "cs", test_part))

  # Calculate mean accuracy grouped by subject and test_part
  accuracy_summary <- cleaned_data %>%
    group_by(subject, test_part) %>%
    summarise(mean_accuracy = mean(accuracy, na.rm = TRUE)) %>%
    filter(test_part == 'cc' | test_part == 'ss')

  return(accuracy_summary)
}

# Apply the function to each dataset
accuracy_compound_prob     <- process_study_data(data_compound_prob)
accuracy_outcome_as_term   <- process_study_data(data_outcome_as_term)
accuracy_number_of_outcome <- process_study_data(data_number_of_outcome)




```










```{r}
# Function to summarize accuracy and perform paired t-test
summarize_accuracy <- function(data) {
  summary_data <- data %>%
    group_by(test_part) %>%
    summarise(
      mean_mean_accuracy = mean(mean_accuracy, na.rm = TRUE),
      sd = sd(mean_accuracy, na.rm = TRUE),
      se = sd(mean_accuracy, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) %>%
    mutate(
      lower = mean_mean_accuracy - 1.96 * se,
      upper = mean_mean_accuracy + 1.96 * se
    )

  # Perform paired t-test between 'cc' and 'ss' conditions
  cc_ss_data <- data %>%
    filter(test_part %in% c("cc", "ss")) %>%
    pivot_wider(names_from = test_part, values_from = mean_accuracy)

  if (all(c("cc", "ss") %in% colnames(cc_ss_data))) {
    t_test <- t.test(cc_ss_data$cc, cc_ss_data$ss, paired = TRUE, alternative = "two.sided")
    t_stat <- t_test$statistic
    p_value <- t_test$p.value
    df <-  t_test$parameter
    significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      )

  } else {
    t_stat <- NA
    p_value <- NA
  }

  summary_data <- summary_data %>%
    mutate(t_statistic = t_stat, p_value = p_value, df = df, significance = significance)

  return(summary_data)
}

# Compute final summary tables
summary_df_cp  <- summarize_accuracy(accuracy_compound_prob)
summary_df_oat <- summarize_accuracy(accuracy_outcome_as_term)
summary_df_no  <- summarize_accuracy(accuracy_number_of_outcome)


```




```{r}
library(dplyr)
library(ggplot2)

# Function to process each dataset
process_catch_choices <- function(data, study_label) {
  test_catch <- data %>%
    filter(skew_level == 'catch') %>%
    filter(test_part == 'ss' | test_part == 'cc') %>%
    mutate(accuracy = case_when(
      EV_diff > 0 & true_response == 'f' ~ 1,
      EV_diff < 0 & true_response == 'j' ~ 1,
      TRUE ~ 0
    ))

  catch_results <- test_catch %>%
    group_by(subject, test_part) %>%
    dplyr::summarize(mean_accuracy = calculate_mean_ci(accuracy)$mean) %>%
    group_by(subject) %>%
    filter(all(c("cc", "ss") %in% test_part)) %>%
    ungroup()


  catch_results_pool <- catch_results %>%
    group_by(test_part) %>%
    dplyr::summarize(mean_accuracy_group = calculate_mean_ci(mean_accuracy)$mean,
              lower = calculate_mean_ci(mean_accuracy)$lower,
              upper = calculate_mean_ci(mean_accuracy)$upper, .groups = "drop") %>%
    mutate(study = study_label)

  catch_results_pivot <- catch_results %>%
    pivot_wider(names_from = test_part, values_from = mean_accuracy, names_prefix = "mean_accuracy_")

  list(catch_results = catch_results, catch_results_pool = catch_results_pool)
}

# Process all three datasets
catch_results_compound_prob     <- process_catch_choices(data_compound_prob,     "compound_prob")
catch_results_outcome_as_term   <- process_catch_choices(data_outcome_as_term,   "outcome-as-term")
catch_results_number_of_outcome <- process_catch_choices(data_number_of_outcome, "number_of_outcome")
```








```{r}
# Catch-trial CC vs SS paired t-tests, using the unified helper.
catch_to_t <- function(catch_results, study_label) {
  cc <- catch_results %>% filter(test_part == "cc") %>% pull(mean_accuracy)
  ss <- catch_results %>% filter(test_part == "ss") %>% pull(mean_accuracy)
  paired_t_test_summary(cc, ss, study_label)
}

t_test_results_catch <- bind_rows(
  catch_to_t(catch_results_compound_prob$catch_results,     "compound_prob"),
  catch_to_t(catch_results_outcome_as_term$catch_results,   "outcome-as-term"),
  catch_to_t(catch_results_number_of_outcome$catch_results, "number_of_outcome")
)

# Combine results
combined_catch_results_pool <- bind_rows(
  catch_results_compound_prob$catch_results_pool,
  catch_results_outcome_as_term$catch_results_pool,
  catch_results_number_of_outcome$catch_results_pool
)


```







Two-sided paired t test comparing participant-level frequency of risky choices in simple versus simple condition against complex versus complex condition.





```{r}
library(dplyr)
library(ggplot2)

# Function to process each dataset
process_risky_choices <- function(data, study_label) {
  test_risky <- data %>%
    filter(skew_level %in% c('right_vs_left', 'left_vs_right', 'no_skew_vs_no_skew')) %>%
    filter(test_part == 'ss' | test_part == 'cc') %>%
    mutate(risky_response = ifelse(true_response == 'f', 1, 0))

  risky_results <- test_risky %>%
    group_by(subject, test_part) %>%
    dplyr::summarize(mean_risky = calculate_mean_ci(risky_response)$mean,
              lower = calculate_mean_ci(risky_response)$lower,
              upper = calculate_mean_ci(risky_response)$upper, .groups = "drop") %>%
    mutate(study = study_label)

  risky_results_pool <- risky_results %>%
    group_by(test_part) %>%
    dplyr::summarize(mean_risky_group = calculate_mean_ci(mean_risky)$mean,
                     sd_risky_group = sd(mean_risky),
              lower = calculate_mean_ci(mean_risky)$lower,
              upper = calculate_mean_ci(mean_risky)$upper, .groups = "drop") %>%
    mutate(study = study_label)

  list(risky_results = risky_results, risky_results_pool = risky_results_pool)
}

# Process all three datasets
results_risky_cp  <- process_risky_choices(data_compound_prob,     "compound_prob")
results_risky_oat <- process_risky_choices(data_outcome_as_term,   "outcome-as-term")
results_risky_no  <- process_risky_choices(data_number_of_outcome, "number_of_outcome")


# Combine results
combined_risky_results_individual <- bind_rows(
  results_risky_cp$risky_results,
  results_risky_oat$risky_results,
  results_risky_no$risky_results
)



# Combine results
combined_risky_results_pool <- bind_rows(
  results_risky_cp$risky_results_pool,
  results_risky_oat$risky_results_pool,
  results_risky_no$risky_results_pool
)

# Risky-choice CC vs SS paired t-tests, using the unified helper.
risky_to_t <- function(risky_results, study_label) {
  cc <- risky_results %>% filter(test_part == "cc") %>% pull(mean_risky)
  ss <- risky_results %>% filter(test_part == "ss") %>% pull(mean_risky)
  paired_t_test_summary(cc, ss, study_label)
}

t_test_results_risky <- bind_rows(
  risky_to_t(results_risky_cp$risky_results,  "compound_prob"),
  risky_to_t(results_risky_oat$risky_results, "outcome-as-term"),
  risky_to_t(results_risky_no$risky_results,  "number_of_outcome")
)
```







Two-sample paired t test comparing participant-level frequency of choosing right skewed lotteries in simple versus simple condition against complex versus complex condition.



```{r}
library(dplyr)
library(purrr)
library(ggplot2)

# Function to process data for one study and conduct detailed t-tests
process_and_ttest <- function(data, study_label) {
  test2 <- data %>%
    filter(skew_level %in% c('right_vs_left', 'left_vs_right')) %>%
    filter(test_part %in% c('cc', 'ss')) %>%
    group_by(subject) %>%
    mutate(choosing_right = ifelse(
      (skew_level == 'left_vs_right' & true_response == 'j') |
      (skew_level == 'right_vs_left' & true_response == 'f'), 1, 0
    ))

  # Summarize proportion of right choices
  right_choice <- test2 %>%
    group_by(subject, test_part) %>%
    summarise(prop_right = mean(choosing_right, na.rm = TRUE), .groups = "drop") %>%
    mutate(study = study_label)

  # Perform paired t-tests for `cc` vs `ss`
  t_test_results <- right_choice %>%
    filter(test_part %in% c("cc", "ss")) %>%
    summarise(
      t_test = list(t.test(
        prop_right[test_part == "cc"],
        prop_right[test_part == "ss"],
        paired = TRUE
      )),
      .groups = "drop"
    ) %>%
    mutate(
      study = study_label,
      t_value = map_dbl(t_test, ~ .x$statistic),
      df = map_dbl(t_test, ~ .x$parameter),
      p_value = map_dbl(t_test, ~ .x$p.value),
      conf_lower = map_dbl(t_test, ~ .x$conf.int[1]),
      conf_upper = map_dbl(t_test, ~ .x$conf.int[2]),
      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      )
    ) %>%
    select(study, t_value, df, p_value, conf_lower, conf_upper,  significance)

  # Calculate group-level means and confidence intervals
  summary_df <- right_choice %>%
    group_by(test_part) %>%
    summarise(
      mean_prop = calculate_mean_ci(prop_right)$mean,
      sd_prop = sd(prop_right),
      lower = calculate_mean_ci(prop_right)$lower,
      upper = calculate_mean_ci(prop_right)$upper,
      .groups = "drop"
    ) %>%
    mutate(study = study_label)

  list(right_choice = right_choice, summary_df = summary_df, t_test_results = t_test_results)
}

# Process all datasets
results_skew_cp  <- process_and_ttest(data_compound_prob,     "compound_prob")
results_skew_oat <- process_and_ttest(data_outcome_as_term,   "outcome-as-term")
results_skew_no  <- process_and_ttest(data_number_of_outcome, "number_of_outcome")



# Combine results
combined_skew_results_individual <- bind_rows(
  results_skew_cp$right_choice,
  results_skew_oat$right_choice,
  results_skew_no$right_choice
)



# Combine summaries and t-test results for plotting
combined_summary_skew <- bind_rows(
  results_skew_cp$summary_df,
  results_skew_oat$summary_df,
  results_skew_no$summary_df
)

combined_ttests_skew <- bind_rows(
  results_skew_cp$t_test_results,
  results_skew_oat$t_test_results,
  results_skew_no$t_test_results
)


```





```{r}
library(cowplot)

# Lookup table from study label to its catch_results object (avoids dynamic
# get() with non-syntactic names like "outcome-as-term").
catch_results_by_study <- list(
  compound_prob     = catch_results_compound_prob,
  `outcome-as-term` = catch_results_outcome_as_term,
  number_of_outcome = catch_results_number_of_outcome
)

generate_combined_study_plot <- function(study_name) {
  # --- RT difference (CC - SS) ---
  plot_mean_rt_group <- combined_mean_rt_group %>% filter(study == study_name)
  plot_individual_rt <- combined_participant_means %>% filter(study == study_name) %>%
    mutate(median_rt_diff = cc - ss)
  plot_t_test_rt <- t_test_results_rt %>% filter(study == study_name)

  plot_rt_diff <- ggplot() +
    geom_point(data = plot_individual_rt,
               aes(x = "CC vs. SS", y = median_rt_diff),
               position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha, color = "black") +
    geom_errorbar(data = plot_mean_rt_group,
                  aes(x = "CC vs. SS", ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = plot_mean_rt_group,
               aes(x = "CC vs. SS", y = mean_rt_diff),
               size = mean_size, color = "black") +
    geom_text(data = plot_t_test_rt,
              aes(x = "CC vs. SS", y = 4.5, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = NULL, y = "RT difference (CC − SS) [s]") +
    ylim(-2, 5) +
    ggtitle("(c) RT difference") +
    theme_psyrev

  # --- EV consistency (model-based) ---
  plot_data_consistency <- combined_consistency %>% filter(study == study_name)
  interaction_study <- interaction_effect_summary %>% filter(study == study_name)

  plot_consistency <- ggplot(plot_data_consistency,
                             aes(x = EV_diff, y = predicted_risk, color = test_part)) +
    geom_line(linewidth = 0.7) +
    geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = test_part),
                alpha = 0.25, color = NA) +
    geom_text(data = interaction_study,
              aes(x = Inf, y = 0.05, label = significance),
              inherit.aes = FALSE, size = sig_text_size, hjust = 1.4, vjust = 0) +
    labs(x = expression(EV[diff]), y = "P(choose A)",
         color = "Trial type", fill = "Trial type") +
    scale_color_manual(values = trial_palette, labels = c(cc = "CC", ss = "SS")) +
    scale_fill_manual(values  = trial_palette, labels = c(cc = "CC", ss = "SS")) +
    ggtitle("(d) EV consistency") +
    theme_psyrev

  # --- Catch-trial accuracy ---
  plot_data_catch <- combined_catch_results_pool %>% filter(study == study_name)
  t_test_catch <- t_test_results_catch %>% filter(study == study_name)
  plot_individual_catch <- catch_results_by_study[[study_name]]$catch_results

  plot_catch <- ggplot() +
    geom_point(data = plot_individual_catch,
               aes(x = test_part, y = mean_accuracy, color = test_part),
               position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha) +
    geom_errorbar(data = plot_data_catch,
                  aes(x = test_part, ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = plot_data_catch,
               aes(x = test_part, y = mean_accuracy_group),
               size = mean_size, color = "black") +
    geom_segment(aes(x = 1, xend = 2, y = 1.07, yend = 1.07),
                 color = "gray30", linewidth = bracket_lw) +
    geom_text(data = t_test_catch,
              aes(x = 1.5, y = 1.11, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0.5, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = "Trial type", y = "Accuracy", color = "Trial type") +
    scale_x_discrete(labels = c(cc = "CC", ss = "SS")) +
    scale_color_manual(values = trial_palette, labels = c(cc = "CC", ss = "SS")) +
    coord_cartesian(ylim = c(0.3, 1.15)) +
    ggtitle("(e) Dominance accuracy") +
    theme_psyrev

  # --- Risky-choice proportion ---
  plot_individual <- combined_risky_results_individual %>% filter(study == study_name)
  plot_summary_risky <- combined_risky_results_pool %>% filter(study == study_name)
  plot_t_test_risky <- t_test_results_risky %>% filter(study == study_name)

  plot_risky <- ggplot() +
    geom_point(data = plot_individual,
               aes(x = test_part, y = mean_risky, color = test_part),
               position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha) +
    geom_errorbar(data = plot_summary_risky,
                  aes(x = test_part, ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = plot_summary_risky,
               aes(x = test_part, y = mean_risky_group),
               size = mean_size, color = "black") +
    geom_segment(aes(x = 1, xend = 2, y = 0.83, yend = 0.83),
                 color = "gray30", linewidth = bracket_lw) +
    geom_text(data = plot_t_test_risky,
              aes(x = 1.5, y = 0.86, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0.5, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = "Trial type", y = "Risky-choice proportion", color = "Trial type") +
    scale_x_discrete(labels = c(cc = "CC", ss = "SS")) +
    scale_color_manual(values = trial_palette, labels = c(cc = "CC", ss = "SS")) +
    coord_cartesian(ylim = c(0.2, 0.9)) +
    ggtitle("(f) Risky-choice difference") +
    theme_psyrev

  # --- Skewness preference ---
  plot_individual_skew <- combined_skew_results_individual %>% filter(study == study_name)
  plot_summary_skew <- combined_summary_skew %>% filter(study == study_name)
  plot_t_test_skew <- combined_ttests_skew %>% filter(study == study_name)

  plot_skew <- ggplot() +
    geom_point(data = plot_individual_skew,
               aes(x = test_part, y = prop_right, color = test_part),
               position = position_jitter(width = 0.18),
               size = point_size, alpha = point_alpha) +
    geom_errorbar(data = plot_summary_skew,
                  aes(x = test_part, ymin = lower, ymax = upper),
                  width = err_w, linewidth = err_lw, color = "black") +
    geom_point(data = plot_summary_skew,
               aes(x = test_part, y = mean_prop),
               size = mean_size, color = "black") +
    geom_segment(aes(x = 1, xend = 2, y = 1.07, yend = 1.07),
                 color = "gray30", linewidth = bracket_lw) +
    geom_text(data = plot_t_test_skew,
              aes(x = 1.5, y = 1.11, label = significance),
              size = sig_text_size, color = "black") +
    geom_hline(yintercept = 0.5, linetype = "dashed",
               color = "gray60", linewidth = hline_lw) +
    labs(x = "Trial type", y = "Right-skewed choice proportion", color = "Trial type") +
    scale_x_discrete(labels = c(cc = "CC", ss = "SS")) +
    scale_color_manual(values = trial_palette, labels = c(cc = "CC", ss = "SS")) +
    coord_cartesian(ylim = c(0.2, 1.15)) +
    ggtitle("(g) Skewness preference") +
    theme_psyrev

  list(
    rt_diff     = plot_rt_diff,
    consistency = plot_consistency,
    catch       = plot_catch,
    risky       = plot_risky,
    skew        = plot_skew
  )
}
```




```{r}
generate_all_subplots <- function(study_name) {
  plot_cs    <- combine_choice_rt_plot(study_name)
  ccss_plots <- generate_combined_study_plot(study_name)

  drop_legend <- theme(legend.position = "none")
  plot_a <- plot_cs$cs_choice + drop_legend
  plot_b <- plot_cs$cs_rt     + drop_legend
  plot_c <- ccss_plots$rt_diff     + drop_legend
  plot_d <- ccss_plots$consistency + drop_legend
  plot_e <- ccss_plots$catch       + drop_legend
  plot_f <- ccss_plots$risky       + drop_legend
  plot_g <- ccss_plots$skew        + drop_legend

  shared_legend <- cowplot::get_legend(
    ccss_plots$skew + theme(legend.position = "bottom")
  )

  # Section dividers
  cs_title   <- ggdraw() + draw_label("CS condition",
                                      fontface = "bold", size = 12,
                                      x = 0.02, hjust = 0)
  ccss_title <- ggdraw() + draw_label("CCSS condition",
                                      fontface = "bold", size = 12,
                                      x = 0.02, hjust = 0)

  # CS row: (a) (b)  — panel letters baked into each plot's ggtitle
  cs_row <- cowplot::plot_grid(plot_a, plot_b, NULL, ncol = 3)

  # CCSS rows: (c)(d)(e) and (f)(g)
  row2 <- cowplot::plot_grid(plot_c, plot_d, plot_e, ncol = 3)
  row3 <- cowplot::plot_grid(plot_f, plot_g, NULL,   ncol = 3)
  ccss_body <- cowplot::plot_grid(row2, row3, ncol = 1, rel_heights = c(1, 1))

  final_plot <- cowplot::plot_grid(
    cs_title, cs_row,
    ccss_title, ccss_body,
    shared_legend,
    ncol = 1,
    rel_heights = c(0.10, 1, 0.10, 2, 0.12)
  )

  ggsave(
    filename = paste0("behavioural_analysis/full_combined_", study_name, ".pdf"),
    plot     = final_plot,
    width    = 17, height = 18, units = "cm",
    dpi      = 600,
    device   = "pdf"
  )
}

lapply(study_names, generate_all_subplots)
```

